\documentclass[11pt, english, letterpaper]{article}
\input{paper/preamble.tex}

\begin{document}
\justifying

% Title ideas 
% Beavers over Brexit
% Beavers or Brexit
% Bigger than Brexit?

\vspace{-2em} 

\title{Bigger than Brexit? \\ Estimating the impact of wildlife reintroduction on land use\thanks{Acknowledgments: I am grateful to Eyal Frank for invaluable feedback. I thank the participants of [discussions] for helpful comments. I acknowledge the generous provision of data by [data providers].}}
% People to recognize:
% Eyal, other readers (Tai, Seth)
% Data providers: NatureScot, AgriStats 

\author[1]{\small Miriam Gold}

\affil[1]{\footnotesize Energy Policy Institute at Chicago, University of Chicago}
\date{\today}
\maketitle

\begin{center}
\vspace{-3em}
\textbf{\textcolor{red}{Preliminary draft. Do not circulate without permission.}}
\end{center}

\begin{abstract}
    \singlespacing 
    Facing environmentally-imposed productivity constraints, including wildlife incursion, economic operations are incentivized to neutralize threats. In the case of wildlife management, such action can often harm social welfare by degrading ecosystem functioning, reducing biodiversity, and eliminating beneficial services provided by culled animals. There remains, however, little empirical evidence on the counterfactual impacts of so-called ``nuisance'' species in the absence of control operations. The beaver (\textit{Castor fiber}), despite producing well-documented benefits as an ecosystem engineer, has long hindered agricultural productivity by inundating fields, grazing crops, and collapsing flood banks. A recent unauthorized reemergence of beavers in Scotland, where they had been driven extinct centuries earlier, has triggered a backlash among agricultural producers, with some claiming the impacts on their industry would be greater than those of Brexit. Using a series of comprehensive regional surveys conducted since beaver reemergence and high-resolution satellite data on land use, I exploit the rapid spread of beavers to measure their impact on the share of land in agricultural use. Contrary to conventional wisdom, preliminary results show an \textit{increase} of 1.7 p.p. (13.6\% relative to baseline) in the share of land devoted to agriculture in 1km$^2$ landscape grid cells. It remains unclear whether the result reflects merely the greening effect of beaver colonization. To verify the environmental mechanism at play, I employ a network of in-situ hydrometry monitoring stations to measure changes in river level and flow following beaver arrival but find inconclusive evidence.
\end{abstract}

\newpage 

\newpage

\input{sections/quote.tex}

\vspace{-5mm} \section{Introduction}
\label{sec:intro}
\input{paper/sections/introduction.tex}

% Background
\section{Background}
\label{sec:background}
\input{sections/background.tex}

% % Data
\section{Data}
\label{sec:data}
\input{sections/data.tex}

% % Empirical Strategy 
\section{Methods}
\label{sec:methods}
\input{sections/methods.tex}

% % Results 
\section{Results}
\label{sec:results}
\input{sections/results.tex}

% \section{Discussion}
% \label{sec:discussion}
% \input{sections/discussion.tex}

\newpage

\printbibliography

% Appendices 
\setcounter{page}{0}
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\renewcommand{\thetable}{\thesection\arabic{table}}
\renewcommand{\thefigure}{\thesection\arabic{figure}}
\renewcommand{\thepage}{\thesection\arabic{page}}
\renewcommand\thesection{\Alph{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\newpage
\section*{Appendix}
\section{Additional Results}
\label{sec:addl_results}
\input{\tabPath/beaver_main/beaver_main_Soverall_table}
\input{\tabPath/beaver_main/beaver_main_Sg2_table.tex}
\input{\tabPath/beaver_main/beaver_main_Sg1_table.tex}
% \input{appendix/additional_results.tex}

% \setcounter{page}{1}
% \setcounter{table}{0}
% \setcounter{figure}{0}
% \renewcommand{\thetable}{\thesection\arabic{table}}
% \renewcommand{\thefigure}{\thesection\arabic{figure}}
% \renewcommand{\thepage}{\thesection\arabic{page}}
% \renewcommand\thesection{\Alph{section}}
% \renewcommand\thesubsection{\thesection.\arabic{subsection}}
% \newpage
% \section{Data Construction}
% \input{appendix/additional_data.tex} 


\begin{comment}
\setcounter{page}{1}
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{\thesection\arabic{table}}
\renewcommand{\thefigure}{\thesection\arabic{figure}}
\renewcommand{\thepage}{\thesection\arabic{page}}
\renewcommand\thesection{\Alph{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\newpage
\section{Supplementary Background on Locusts' Biology}
\input{appendix/additional_background}
\end{comment}

\end{document}
